%-------------------------------------
% LaTeX Resume for Software Engineers
% Author : Leslie Cheng
% License : MIT
%-------------------------------------

\documentclass[letterpaper,12pt]{article}

\usepackage[empty]{fullpage}
\usepackage{enumitem}
\usepackage{ifxetex}
\usepackage{makecell}
\ifxetex
\usepackage{fontspec}
\usepackage[xetex]{hyperref}
\else
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[pdftex]{hyperref}
\fi
\usepackage{fontawesome}
\usepackage[sfdefault,light]{FiraSans}
\usepackage{anyfontsize}
\usepackage{xcolor}
\usepackage{tabularx}

%-------------------------------------------------- SETTINGS HERE --------------------------------------------------
% Header settings
\def \fullname {Ali Satvaty}
\def \subtitle {Computer Engineer}

\def \phoneicon {\faPhone}
\def \phonetext {(+98) 9155192078}

\def \skypeicon {\faSkype}
\def \skypetext {live:1}

\def \emailicon {\faEnvelope}
\def \emaillink {mailto:alistvt@gmail.com}
\def \emailtext {alistvt@gmail.com}

\def \githubicon {\faGithub}
\def \githublink {https://github.com/alistvt}
\def \githubtext {/alistvt}

\def \linkedinicon {\faLinkedin}
\def \linkedinlink {https://www.linkedin.com/in/alistvt}
\def \linkedintext {/alistvt}

\def \headertype {\singlecol} % \singlecol or \doublecol

% Misc settings
\def \entryspacing {-0pt}

\def \bulletstyle {\faAngleRight}

% Define colours
\definecolor{primary}{HTML}{000000}
\definecolor{secondary}{HTML}{0D47A1}
\definecolor{accent}{HTML}{263238}
\definecolor{links}{HTML}{1565C0}

%------------------------------------------------------------------------------------------------------------------- 

% Defines to make listing easier
\def \linkedin {\linkedinicon \hspace{3pt}\href{\linkedinlink}{\linkedintext}}
\def \phone {\phoneicon \hspace{3pt}{ \phonetext}}
\def \email {\emailicon \hspace{3pt}\href{\emaillink}{\emailtext}}
\def \github {\githubicon \hspace{3pt}\href{\githublink}{\githubtext}}
\def \address {\addressicon \hspace{3pt}{\addresstext}}
\def \skype {\skypeicon \hspace{3pt}{ \skypetext}}

% Adjust margins
\addtolength{\oddsidemargin}{-0.55in}
\addtolength{\evensidemargin}{-0.55in}
\addtolength{\textwidth}{1.1in}
\addtolength{\topmargin}{-0.6in}
\addtolength{\textheight}{1.1in}

% Define the link colours
\hypersetup{
	colorlinks=true,
	urlcolor=links,
}

% Set the margin alignment 
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

%-------------------------
% Custom commands

% Sections
\renewcommand{\section}[2]{\vspace{5pt}
	\colorbox{secondary}{\color{white}\raggedbottom\normalsize\textbf{{#1}{\hspace{7pt}#2}}}
}

% Entry start and end, for spacing
\newcommand{\resumeEntryStart}{\begin{itemize}[leftmargin=2.5mm]}
	\newcommand{\resumeEntryEnd}{\end{itemize}\vspace{\entryspacing}}

% Itemized list for the bullet points under an entry, if necessary
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=4.5mm]}
	\newcommand{\resumeItemListEnd}{\end{itemize}}

% Resume item
\renewcommand{\labelitemii}{\bulletstyle}
\newcommand{\resumeItem}[1]{
	\item\small{
		{#1 \vspace{-2pt}}
	}
}

% Entry with title, subheading, date(s), and location
\newcommand{\resumeEntryTSDL}[4]{
	\vspace{-1pt}\item[]
	\begin{tabularx}{0.97\textwidth}{X@{\hspace{60pt}}r}
		\textbf{\color{primary}#1} & {\firabook\color{accent}\small#2} \\
		\textit{\color{accent}\small#3} & \textit{\color{accent}\small#4} \\
	\end{tabularx}\vspace{-6pt}
}

% Entry with title and date(s)
\newcommand{\resumeEntryTD}[2]{
	\vspace{-1pt}\item[]
	\begin{tabularx}{0.97\textwidth}{X@{\hspace{60pt}}r}
		\textbf{\color{primary}#1} & {\firabook\color{accent}\small#2} \\
	\end{tabularx}\vspace{-6pt}
}

% Entry for special (skills)
\newcommand{\resumeEntryS}[2]{
	\item[]\small{
		\textbf{\color{primary}#1 }{ #2 \vspace{-6pt}}
	}
}

\newcommand{\resumeEntryTSDLP}[5]{
	\vspace{-1pt}\item[]
	\begin{tabularx}{0.97\textwidth}{X@{\hspace{60pt}}r}
		\textbf{\color{primary}#1}{ #2 \vspace{-6pt}} & {\firabook\color{accent}\small#3} \\
		\textit{\color{accent}\small#4} & \textit{\color{accent}\small#5} \\
	\end{tabularx}\vspace{-6pt}
}

% Double column header
\newcommand{\doublecol}[6]{
	\begin{tabularx}{\textwidth}{Xr}
		{
			\begin{tabular}[c]{l}
				\fontsize{35}{45}\selectfont{\color{primary}{{\textbf{\fullname}}}} \\
				%{\textit{\subtitle}} % You could add a subtitle here
			\end{tabular}
		} & {
			\begin{tabular}[c]{l@{\hspace{1.5em}}l}
				{\small#4} & {\small#1} \\
				{\small#5} & {\small#2} \\
				{\small#6} & {\small#3}
			\end{tabular}
		}
	\end{tabularx}
}

% Single column header
\newcommand{\singlecol}[6]{
	\begin{tabularx}{\textwidth}{Xr}
		{
			\begin{tabular}[b]{l}
				\fontsize{35}{45}\selectfont{\color{primary}{{\textbf{\fullname}}}} \\
				%{\textit{\subtitle}} % You could add a subtitle here
			\end{tabular}
		} & {
			\begin{tabular}[c]{l}
				{\small#1} \\
				{\small#2} \\
				{\small#3} \\
				{\small#4} \\
				{\small#5} \\
				{\small#6}
			\end{tabular}
		}
	\end{tabularx}
}

\begin{document}
	%-------------------------------------------------- BEGIN HERE --------------------------------------------------
	
	%---------------------------------------------------- HEADER ----------------------------------------------------
	
	\headertype{\email}{\linkedin}{\github}{}{}{} % Set the order of items here
	\vspace{-10pt} % Set a negative value to push the body up, and the opposite
	
	
	
	%-------------------------------------------------- RESEARCH INTERESTS --------------------------------------------------
	
	\section{\faQuestion}{Research Interests}
	\resumeEntryStart
	\resumeEntryS
	{Natural Language Processing, Deep Learning, Machine Learning, Artificial Intelligence}{}
	\resumeEntryEnd
	
	%-------------------------------------------------- EDUCATION --------------------------------------------------
	\section{\faGraduationCap}{Education}
	\resumeEntryStart
	\resumeEntryTSDL
	{M.Sc. in Artificial Intelligence and Robotics}{2020 - Present}{Expecting to graduate in Jan. 2023}
	{Sharif University of Technology, Tehran, Iran (SUT)}
	\resumeItemListStart
	\resumeItem {Currently Studying in the 4th semester with GPA 17.52/20}
	\resumeItem {Course Highlights: Natural Language Processing, Machine Learning, Deep Learning, Digital Signal Processing, Speech Recognition, Artificial Intelligence}
	\resumeItemListEnd
	\resumeEntryEnd
	
	\resumeEntryStart
	\resumeEntryTSDL
	{B.Sc. in Control and Robotics - Electrical Engineering}{2014 - 2019}
	{Graduated among the top students}{Tehran University, Iran (UT)}
	\resumeItemListStart
	\resumeItem {Graduated with GPA 17.02/20}
	\resumeItem {Course Highlights: Advanced Programming, Microprocessors, Advanced Control Systems, Computer Architecture, Linear Algebra}
	\resumeItemListEnd
	\resumeEntryEnd
	
	%-------------------------------------------------- HONORS and AWARDS --------------------------------------------------
	\section{\faTrophy}{Honors and Awards}
	
	\resumeEntryStart
	\resumeEntryTD
	{Ranked \textbf{$12_{th}$} between \textbf{$ 35,000 $} in Iran national master's entrance exam}{2020}
	\resumeEntryEnd
	
	\resumeEntryStart
	\resumeEntryTD
	{Received scholarship from faculty of Engineering as an exceptional talent student.}{2018}
	\resumeEntryEnd
	
	\resumeEntryStart
	\resumeEntryTD
	{Ranked \textbf{ $1_{st} $} in Sharif University of Technology’s Bot Cup contest.}{2018}
	\resumeEntryEnd
	
	\resumeEntryStart
	\resumeEntryTD
	{Received scholarship from faculty of Engineering as an exceptional talent student.}{2017}
	\resumeEntryEnd
	
	\resumeEntryStart
	\resumeEntryTD
	{Ranked \textbf{$ 194_{th} $} between \textbf{$ 200,000 $} in Iran national University Entrance Exam (Konkour)}{2016}
	\resumeEntryEnd
	
	\resumeEntryStart
	\resumeEntryTD
	{Membership in National Organization for Development of Exceptional Talents (NODET)}{2007-2014}
	\resumeEntryEnd
	
	
	\section{\faShirtsinbulk}{Certificates}
	
	\resumeEntryStart
	\resumeEntryTD
	{Neural Networks and Deep Learning}{\href{https://www.coursera.org/account/accomplishments/verify/YWSYWM5T2MXC?utm_source=link&utm_medium=certificate&utm_content=cert_image&utm_campaign=sharing_cta&utm_product=course}{Coursera}}
	\resumeEntryEnd
	
	\resumeEntryStart
	\resumeEntryTD
	{Natural Language Processing with Classification and Vector Spaces}{\href{https://coursera.org/share/e4928f4bf88e54e314d6b42d485ecc0f}{Coursera}}
	\resumeEntryEnd

	\resumeEntryStart
	\resumeEntryTD
	{Natural Language Processing with Sequence Models}{\href{https://coursera.org/share/b6460e3fd5fa65d841e91b671fdc41c0}{Coursera}}
	\resumeEntryEnd	
	
	%-------------------------------------------------- EXPERIENCES --------------------------------------------------
	
	\section{\faBook}{Research Background}
	\resumeEntryStart
	\resumeEntryTSDL
	{Research on ''Conversational Question Answering''}{Jan. 2021 - Present}
	{I am currently working on this project as my M.Sc. thesis under the supervision of Prof. Hossein Sameti. In this project we are trying to enhance the history selection module, presented in the conversational question answering systems.}{SUT}
	\resumeEntryEnd
	
	\resumeEntryStart
	\resumeEntryTSDL
	{Research on ''3-DoF Delta Robot''}{July 2020 - Oct. 2020}
	{I worked on this project as my B.Sc. internship task under the supervision of Prof. Mehid Tale Masoule. In this project, especially I was working on the artificial intelligence part of the system. At first, 
		we created a conveyor belt system, and then we designed a vision system for the process of 
		pick-and-place. The robot was able to detect special but simple objects using image processing 
		in Matlab and pick them up using suction.}{UT}
	\resumeEntryEnd
	
	
	\section{\faPieChart}{Experiences}
	
	\resumeEntryStart
	\resumeEntryTSDL
	{Freelance Python Developer}{2017 - present}
	{I have done lots of projects as a freelancer, most of which being web development. Some of my projects are open-source and available in my GitHub.}{}
	\resumeEntryEnd
	
	\resumeEntryStart
	\resumeEntryTSDL
	{Internship, Backend Developer}{2019}
	{I spent a 5 months internship in Idearun co. as a backend developer. In my 
		internship program, I worked on two web projects. }{Indearun co.}
	\resumeEntryEnd
	
	
	
	\section{\faGroup}{Teaching Assistant}
	
	\resumeEntryStart
	\resumeEntryTSDL
	{Security in Machine Learning }{2021}
	{Dr. Rohban}{SUT}
	\resumeEntryEnd
	
	\resumeEntryStart
	\resumeEntryTSDL
	{Communication Systems I}{2017}
	{Dr. Abbasfar}{UT}
	\resumeEntryEnd
	
	\resumeEntryStart
	\resumeEntryTSDL
	{Linear Control Systems Laboratory}{2016}
	{Dr. Abbasian}{UT}
	\resumeEntryEnd
	
	\resumeEntryStart
	\resumeEntryTSDL
	{Electrical Circuits I Laboratory}{2015}
	{Dr. Rashed Mohassel}{UT}
	\resumeEntryEnd
	
	
	%-------------------------------------------------- PROJECTS and STUDIES--------------------------------------------------
	\section{\faFlask}{Related Course Projects}
	\resumeEntryStart
	\resumeEntryTD
	{Speech Recognition}{Dr. Sameti}
	\resumeItemListStart
	\resumeItem {Emotion recognition from speech}
	\resumeItemListEnd
	\resumeEntryEnd
	
	\resumeEntryStart
	\resumeEntryTD
	{Natural Language Processing}{Dr. Bokaie}
	\resumeItemListStart
	\resumeItem {Smart chat-bot implementation using retrieval and generative methods.}
	\resumeItemListEnd
	\resumeEntryEnd
	
	\resumeEntryStart
	\resumeEntryTD
	{Advanced Programming}{Dr. Khosravi}
	\resumeItemListStart
	\resumeItem {Design and programming of an Uber-like taxi reserving system.}
	\resumeItemListEnd
	\resumeEntryEnd
	
	\resumeEntryStart
	\resumeEntryTD
	{Microprocessors}{Dr. Fatemi}
	\resumeItemListStart
	\resumeItem {Designing and implementing an Automatic Vaccum Cleaner}
	\resumeItemListEnd
	\resumeEntryEnd
	
	\resumeEntryStart
	\resumeEntryTD
	{Industrial Control}{Dr. Kalhor}
	\resumeItemListStart
	\resumeItem {Stabilization of a balls’ height in a vertical pipe}
	\resumeItemListEnd
	\resumeEntryEnd

	\resumeEntryStart
	\resumeEntryTD
	{Digital Logic Design}{Dr. Navabi}
	\resumeItemListStart
	\resumeItem {Implementing a digital oscilloscope on FPGA}
	\resumeItemListEnd
	\resumeEntryEnd	
	%-------------------------------------------------- PROGRAMMING SKILLS --------------------------------------------------
	\section{\faGears}{Skills}
	\resumeEntryStart
	\resumeEntryS{Languages } {Persian (Native), English (TOEFL 99)}
	\resumeEntryS{Programming } {Python, C++/C, Javascript, MATLAB}
	\resumeEntryS{Machine Learning } {Transformers, Huggingface, Pytorch, Trax, NumPy, pandas, scikit-learn, matplotlib}
	\resumeEntryS{Software \& Tools } {Microsoft Office, Photoshop}
	\resumeEntryS{Web } {React, Django}
	\resumeEntryS{Databases } {MySQL, PostgreSQL, Redis, Mongodb, Sqlite}
	\resumeEntryS{Operating Systems } {Linux, Windows}
	\resumeEntryS{Others } {Latex, Git}
	\resumeEntryEnd
	
	
	\section{\faArrowCircleUp}{Reference Contacts}
	\resumeEntryStart
	\resumeEntryTSDLP{\faEnvelope \space \space \space Prof. Hossein Sameti} {sameti@sharif.ir}{}{Professor, Department of Computer Engineering, Sharif University of Technology}{}
	\resumeEntryTSDLP{\faEnvelope \space \space \space Prof. Mehdi Tale Masoule} {m.t.masouleh@ut.ac.ir}{}{Professor, Department of Electrical and Computer Engineering, Tehran University of Tehran}{}
	\resumeEntryEnd
	
\end{document}